Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-12 submission/appendix.tex
results added

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  78 \\
svhn          &  30 \\
cifar-100     &  30 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used}
\label{table:datasets}
\end{table}

@@

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  78 \\
svhn          &  30 \\
cifar-100     &  30 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used}
\label{table:datasets}
\end{table}`

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & 3.51 & 4.01 \\
 cifar-10 & ResNet  & 0.31 &  0.30 & 0.28 & 0.28 \\
 cifar-100 & ResNet  & 4.13 &  4.50 & 3.06 & 3.06 \\
 svhn & ResNet  & 0.04 &  0.04 & 0.02 & 0.02 \\
 cub-200-2011 & ResNet  & 0.20 &  0.18 & 3.19 & 3.21 \\
 imagenet-1k & EfficientNet  & 9.25 &  9.28 & 9.28 & 9.27 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & 3.59 & 3.71 \\
 imagenet-1k & VGG  & 0.84 &  0.68 & 1.89 & 1.59 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & 18.48 \\
 imagenet-1k & DLA  & 22.41 &  8.49 & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & 0.16 & 0.16 \\
 imagenet-1k & DRN  & 0.60 &  0.66 & 0.40 & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & 13.23 \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & 1.87 & 2.53 \\
 imagenet-1k & ProxylessNAS  & 0.19 &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & 0.07 & 0.08 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & 1.09 \\
 cifar-10 & DIA-ResNet  & 0.05 &  0.08 & 0.28 & 0.32 \\
 cifar-100 & DIA-ResNet  & 0.36 &  1.38 & 0.93 & 1.02 \\
 svhn & DIA-ResNet  & 0.00 &  0.00 & 0.02 & 0.02 \\
 cifar-10 & SENet  & 0.09 &  0.09 & 0.04 & 0.04 \\
 cifar-100 & SENet  & 0.36 &  0.43 & 0.26 & 0.26 \\
 svhn & SENet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 cub-200-2011 & SENet  & 1.07 &  1.29 & 1.85 & 1.95 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & 0.06 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & 0.01 \\
 cifar-100 & ResNeXt  & 0.80 &  0.95 & 0.78 & 0.79 \\
 svhn & ResNeXt  & 0.00 &  0.00 & 0.01 & 0.01 \\
\hline
\end{tabular}
\end{center}
\caption{MSE Results}
\label{table:MSEresults}
\end{table}`

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
Dataset & Model & Fnorm & Snorm & wAlpha & aNorm \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & 0.90 & 0.88 \\
 cifar-10 & ResNet  & 0.58 &  0.59 & 0.62 & 0.61 \\
 cifar-100 & ResNet  & 0.61 &  0.58 & 0.71 & 0.71 \\
 svhn & ResNet  & 0.69 &  0.70 & 0.82 & 0.81 \\
 cub-200-2011 & ResNet  & 0.94 &  0.95 & 0.08 & 0.08 \\
 imagenet-1k & EfficientNet  & 0.00 &  0.00 & 0.00 & 0.00 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & 0.85 & 0.85 \\
 imagenet-1k & VGG  & 0.71 &  0.76 & 0.35 & 0.45 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & 0.81 \\
 imagenet-1k & DLA  & 0.13 &  0.67 & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & 0.97 & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & 0.87 & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & 0.43 \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & 0.92 & 0.89 \\
 imagenet-1k & ProxylessNAS  & 0.68 &  0.56 & 0.53 & 0.58 \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & 0.38 & 0.26 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & 0.99 \\
 cifar-10 & DIA-ResNett  & 0.96 &  0.93 & 0.74 & 0.71 \\
 cifar-100 & DIA-ResNet  & 0.96 &  0.85 & 0.90 & 0.89 \\
 svhn & DIA-ResNet  & 0.94 &  0.95 & 0.78 & 0.77 \\
 cifar-10 & SENet  & 0.91 &  0.91 & 0.96 & 0.96 \\
 cifar-100 & SENet  & 0.97 &  0.96 & 0.98 & 0.98 \\
 svhn & SENet & 0.99 &  0.96 & 0.98 & 0.98 \\
 cub-200-2011 & SENet  & 0.66 &  0.59 & 0.41 & 0.38 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & 0.69 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & 0.21 \\
 cifar-100 & ResNeXt  & 0.17 &  0.02 & 0.20 & 0.18 \\
 svhn & ResNeXt  & 0.87 &  0.90 & 0.64 & 0.75 \\
\hline
\end{tabular}
\end{center}
\caption{$R^{2}$ Results}
\label{table:R2results}
\end{table}`
